Mechanical loading prediction through accelerometry data during walking and running

### 2021-10-01 manuscript/manuscript.Rmd
Format manuscript to submit to JSHS

---
title: "Mechanical loading prediction through accelerometry data during walking and running"
output:
  bookdown::pdf_document2:
    toc: false
    includes:
      in_header: "preamble.tex"
    latex_engine: lualatex
  word_document:
    reference_docx: style_reference.docx
always_allow_html: true
bibliography: bibliography.bib
csl: nlm.csl
---

@@

# Introduction {.unnumbered}

@@

# Methods {.unnumbered}

## Participants {.unnumbered}

@@

## Data collection protocol {.unnumbered}

@@

## Data processing {.unnumbered}

@@

## Statistical analyses {.unnumbered}

@@

# Results {.unnumbered}

@@

# Discussion {.unnumbered}

@@

>>>>

---
title: "Mechanical loading prediction through accelerometry data during walking and running"
output:
  bookdown::pdf_document2:
    toc: false
    includes:
      in_header: "preamble.tex"
    latex_engine: lualatex
  word_document:
    reference_docx: style_reference.docx
always_allow_html: true
bibliography: bibliography.bib
csl: ama.csl
---

@@

# Introduction

@@

# Methods

## Participants

@@

## Data collection protocol

@@

## Data processing

@@

## Statistical analyses

@@

# Results

@@

# Discussion

@@

# Conclusion
